plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-10-12 manuscript.Rmd
Final minor revisions

\
In the practical application of the FvCB model, when leaf gas exchange is measured with a portable gas exchange instrument, estimates of C~c~ are difficult to obtain because they require an estimate of the mesophyll conductance. In this case, it is customary to us the intercellular [CO~2~] concentration (C~i~) as the driver of photosynthesis. This approach is useful because C~i~ can be estimated from concurrent measurements of CO~2~ and H~2~O flux [@sharkey1982]. In the remainder of this article I will use C~c~ as the driver of photosynthesis, but point out that this can be replaced by C~i~ if the user does not have an estimate of g~m~. When this is is known, C~c~ is calculated from C~i~ with Eq. 2.

@@

\
**Figure 1**. (a) Leaf photosynthesis - CO~2~ response curve as modelled with the FvCB model. (b) The intersection of the supply and demand curves of photosynthesis. The `Photosyn` function solves for C~c~ if g~s~, V~cmax~, J~max~ and R~d~ (and other parameters to the FvCB model) are known.

@@

The intersection of the supply and demand curves of photosynthesis (Fig. 1b) gives the steady-state intercellular CO~2~ concentration (C~i~). This is solved by the `Photosyn` function. This flexible interface can be used to either 1) estimate A~n~ when C~i~ is known (`Photosyn(Ci=...)`, equivalent to `Aci(...)`), 2) estimate A~n~ when g~s~ is known (`Photosyn(GS=...)`) (cf. Fig. 1b) or c) solve for C~i~ from the coupled leaf gas exchange model (Eqs. 1,3,4).

\
To demonstrate the use of the coupled gas exchange model, I visualize the temperature response of A~n~ when both T~leaf~ and D are varying. In field conditions, D is always strongly positively related to T~leaf~. The consequence is that when studying D or T~leaf~ responses in the field, both drivers have to be accounted for simultaneously [@lin2012; @duursma2014]. Figure 3a shows simulated A-C~i~ curves and the solutions of the coupled leaf gas exchange models at a range of T~leaf~ and corresponding D (calculated following [@duursma2014]). Both V~cmax~ and J~max~ have a peaked response to T~leaf~, so that at a given C~i~, A~n~ first increases with T~leaf and then decreases (lines, Fig. 3a). As a result of increasing D, the modelled C~i~ decreases (symbols, Fig. 3a). The net result is a peaked response of A~n~ as a function of D (Fig. 3b).

@@

The simplified code to produce Figure 3b, using the `Photosyn` function, is given below. Note that in this example the default values of many parameters (e.g. J~max~, g~1~) are used in the call to `Photosyn`, but all of these can be set by the user.

@@

To find optimal stomatal conductance, `FARAO` finds the C~i~ for which the quantity $A_n - \lambda E$ is maximal, where E is the leaf transpiration rate and $\lambda$ is the marginal cost of water (an empirical parameter related to g~1~, see [@medlyn2011]). A~n~ is calculated directly as a function of C~i~ via the FvCB model (Eq. 1), g~s~ is calculated by rearranging Eq. 3, and E is calculated assuming perfect coupling (thus $E = g_s D/P_a$, where P~a~ is atmospheric pressure). This numerical routine does not need specification of an f(D) function as in Eq. 4, instead, this function is an emergent property.  In Fig. 4a, I have calculated $A_n - \lambda E$ across a range of C~i~ values, and for different values of D. The `FARAO` function calculates the optima of these curves, which can for example be used to study the response of stomatal conductance to D (Fig. 4b).

@@

To demonstrate a practical application of the key functions in the package, I use field-collected data from Medlyn et al. [-@medlyn2007, @medlynfigshare] on *Eucalyptus delegatensis*. Both A-C~i~ curves and 'spot gas exchange' data (i.e. leaf gas exchange measurements at prevailing environmental conditions) were collected. Using the `fitacis` function, it is straightforward to fit all `r length(acifits)` curves to the A-C~i~ data, and make standard plots of the fitted curves (shown in Fig. 5a). The fitted coefficients can be extracted using the `coef` function, and used to plot a comparison of fitted V~cmax~ and J~max~ values, which show the typical correlation between the two (Fig. 5b).

>>>>

\
In the practical application of the FvCB model, when leaf gas exchange is measured with a portable gas exchange instrument, estimates of C~c~ are difficult to obtain because they require an estimate of the mesophyll conductance (g~m~). In this case, it is customary to us the intercellular [CO~2~] concentration (C~i~) as the driver of photosynthesis. This approach is useful because C~i~ can be estimated from concurrent measurements of CO~2~ and H~2~O flux [@sharkey1982]. In the remainder of this article I will use C~c~ as the driver of photosynthesis, but point out that this can be replaced by C~i~ if the user does not have an estimate of g~m~. When g~m~ is known, C~c~ is calculated from C~i~ with Eq. 2.

@@

\
**Figure 1**. (a) Leaf photosynthesis - CO~2~ response curve as modelled with the FvCB model. (b) The intersection of the supply and demand curves of photosynthesis. The `Photosyn` function solves for C~i~ if g~s~, V~cmax~, J~max~ and R~d~ (and other parameters to the FvCB model) are known.

@@

The intersection of the supply and demand curves of photosynthesis (Fig. 1b) gives the steady-state intercellular CO~2~ concentration (C~i~). This is solved by the `Photosyn` function. This flexible interface can be used to either 1) estimate A~n~ when C~i~ is known (`Photosyn(Ci=...)`; equivalent to `Aci(...)`), 2) estimate A~n~ when g~s~ is known (`Photosyn(GS=...)`) (cf. Fig. 1b) or c) solve for C~i~ from the coupled leaf gas exchange model (Eqs. 1,3,4).

\
To demonstrate the use of the coupled gas exchange model, I visualize the temperature response of A~n~ when both T~leaf~ and D are varying. In field conditions, D is always strongly positively related to T~leaf~. The consequence is that when studying D or T~leaf~ responses in the field, both drivers have to be accounted for simultaneously [@lin2012; @duursma2014]. Figure 3a shows simulated A-C~i~ curves and the solutions of the coupled leaf gas exchange models at a range of T~leaf~ and corresponding D (calculated following [@duursma2014]). Both V~cmax~ and J~max~ have a peaked response to T~leaf~, so that at a given C~i~, A~n~ first increases with T~leaf~ and then decreases (lines, Fig. 3a). As a result of increasing D, the modelled C~i~ decreases (symbols, Fig. 3a, as a consequence of Eq. 4). The net result is a peaked response of A~n~ as a function of D (Fig. 3b).

@@

\
The simplified code to produce Figure 3b, using the `Photosyn` function, is given below. Note that in this example the default values of many parameters (e.g. J~max~, g~1~) are used in the call to `Photosyn`, but all of these can be set by the user.

@@

To find optimal stomatal conductance, `FARAO` finds the C~i~ for which the quantity $A_n - \lambda E$ is maximal, where E is the leaf transpiration rate and $\lambda$ is the marginal cost of water (an empirical parameter related to g~1~, see [@cowan1977; @medlyn2011]). A~n~ is calculated directly as a function of C~i~ via the FvCB model (Eq. 1), g~s~ is calculated by rearranging Eq. 3, and E is calculated assuming perfect coupling (thus $E = g_s D/P_a$, where P~a~ is atmospheric pressure). This numerical routine does not need specification of an f(D) function as in Eq. 4, instead, this function is an emergent property.  In Fig. 4a, I have calculated $A_n - \lambda E$ across a range of C~i~ values, and for different values of D. The `FARAO` function calculates the optima of these curves, which can for example be used to study the response of stomatal conductance to D (Fig. 4b).

@@

To demonstrate a practical application of the key functions in the package, I use field-collected data from Medlyn et al. [@medlyn2007; @medlynfigshare] on *Eucalyptus delegatensis*. Both A-C~i~ curves and 'spot gas exchange' data (i.e. leaf gas exchange measurements at prevailing environmental conditions) were collected. Using the `fitacis` function, it is straightforward to fit all `r length(acifits)` curves to the A-C~i~ data, and make standard plots of the fitted curves (shown in Fig. 5a). The fitted coefficients can be extracted using the `coef` function, and used to plot a comparison of fitted V~cmax~ and J~max~ values, which show the typical correlation between the two (Fig. 5b).
